A Real-Time Sonar Simulator for Automatic Target Recognition

### 2015-10-07 Simulator/article.tex
la2pdf commit - 2015:10:07	11:53:29	(Wed 7.Oct)

% NOTE: PDF hyperlink and bookmark features are not required in IEEE
%       papers and their use requires extra complexity and work.
% \newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true,
% pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
% colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
% pdftitle={Optimal Window Design for the Low Complexity Adaptive Beamformer in Active Sonar Imaging},
% pdfsubject={},
% pdfauthor={Jo Inge Buskenes},
% pdfkeywords={adaptive beamforming, beamforming, complexity, sonar, active}}%
\ifCLASSINFOpdf
%    \usepackage[\MYhyperrefoptions,pdftex]{hyperref}
   \usepackage[pdftex,
    final,                %Keep hyperlink stuff even when in draft mode
    breaklinks=true,      %Break links when necessary
    linktocpage=true,     %Enable link to page?
    linkcolor=black,  %Colour of links to labels within document
    citecolor=black,      %Colour of links to the biliography
    filecolor=red,        %Colour of links to local files
    pagecolor=black,        %Colour of links to other pages withing document
    urlcolor=Blue,        %Colour of the links to external URLs
    colorlinks=true,      %??
    plainpages=false,     %Store roman/arabic numbering differently to avoid
    bookmarksnumbered ]{hyperref}

\else
   \usepackage[\MYhyperrefoptions,breaklinks=true,dvips]{hyperref}
   \usepackage{breakurl}                        % Allows 'dvips' driver to break links
\fi

@@

% \usepackage[maxfloats=40]{morefloats}
\newcounter{todoidx}
% \setcounter{todoidx}

\ifTODO
   \definecolor{todobackground}{rgb}{0.95,0.95,0.95}
   \setlength\marginparsep{1pt}
   \setlength\marginparwidth{35pt}
   \newlength\marginparwidthsmall
   \setlength\marginparwidthsmall{\marginparwidth}
   \addtolength\marginparwidthsmall{-7pt}
   \newcommand\todo[1]{%
      \addtocounter{todoidx}{1}%
      {\color{Red}\bf(\thetodoidx{})}%%\fbox{\bf\thetodoidx{}}}%
      \marginpar{%
         {\vspace*{-10pt}\color{Red}\fbox{\bf\thetodoidx{}}}\\%
         \fcolorbox{red}{todobackground}{\parbox{\marginparwidthsmall}{\raggedright\scriptsize #1}}}}

@@

% \usepackage{float}

@@

\newcommand\Fig[1]{Fig.~\ref{#1}}
\newcommand\eq[1]{(\ref{#1})}

@@

\newcommand\Om{O_\text{m}}
\newcommand\Oa{O_\text{a}}
\newcommand\Nl{N_\text{l}}
\newcommand\Nk{N_\text{k}}
\newcommand\1{\vec 1}
\newcommand\I{\mat I}
\renewcommand*\a{\vec a}
\newcommand*\f{\vec f}
\renewcommand*\i{\vec i}
\renewcommand*\k{\vec k}
\newcommand*\n{\vec n}
\newcommand*\p{\vec p}
\newcommand*\s{\vec s}
\newcommand*\w{\vec w}
\newcommand*\x{\vec x}
\newcommand*\y{\vec y}

@@

\renewcommand\argmin{\text{argmin}}

@@

\newcommand\minus{\scalebox{0.75}[1.0]{$-$}}

% \usepackage{tikz}
% \usetikzlibrary{shapes,snakes}
\usepackage{amsmath,amssymb}

@@

\begin{figure}[tbp]\centering%
\graphicsAI[drawing,width=\linewidth]{gfx/specs.svg}%
\caption{Simulator specifications.}\label{specs}%
\end{figure}

@@

\begin{figure*}[h]\centering%
\subfloat[SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.]{%
\graphicsAI[drawing,width=0.5\linewidth]{gfx/data_cylinder_submerged.svg}%
\label{data_cylinder}}%
\subfloat[Cylinder simulation with parameters estimated from SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.]{
\graphicsAI[drawing,width=0.5\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
\label{sim_cylinder}}%
\caption{A SAS image of a cylinder and a template simulation adapted to it.}
\end{figure*}

@@

\begin{figure*}[!tb]\centering%

\subfloat[Best template out of a predefined set. Inaccurate cylinder length, alignment and immersion depth. The segmented shadow and highlight regions are misaligned.]{
\graphicsAI[drawing,width=.5\linewidth]{gfx/overlay_cylinder_submerged.svg}\label{overlay_cylinder}%
}%
\hfil%
\subfloat[Adapted template. Template simulated with adapted parameters. Good fit in both highlight and shadow segments.]{%
\graphicsAI[width=.5\linewidth]{gfx/overlay_cylinder_submerged_adaptive.svg}%
}\caption{Segmented simulation image overlaid the segmented SAS image. Segmentation overlay color description:\newline
% \hfill
% \parbox{1cm}{\small\centering
% \newline\centering\newline %\\[.5\baselineskip]
% \begin{minipage}{.35\linewidth}
% \cdesc{800000}{Template highlight and image highlight}
% \cdesc{FF1000}{Template highlight only}
% \cdesc{FFEB00}{Image highlight only}
% \cdesc{83FF7C}{Background pixels}
% \end{minipage}%
% \begin{minipage}{.35\linewidth}
% \cdesc{000083}{Template shadow and image shadow}
% \cdesc{0014FF}{Template shadow only}
% \cdesc{00EFFF}{Image shadow only}
% \cdesc{00A7FF}{Template shadow and image highlight}
% \end{minipage}
}\label{overlay_cylinder_adaptive}%
% % \vspace{\baselineskip}
\caption{Segmented simulation image overlaid the segmented SAS image.}
\end{figure*}

>>>>

% NOTE: PDF hyperlink and bookmark features are not required in IEEE
%       papers and their use requires extra complexity and work.
\newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true,
pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
pdftitle={A Fast GPU Sonar Simulator for Automatic Target Recognition},
pdfsubject={},
pdfauthor={Jo Inge Buskenes},
pdfkeywords={adaptive beamforming, beamforming, complexity, sonar, active}}%
\ifCLASSINFOpdf
   \usepackage[\MYhyperrefoptions,pdftex]{hyperref}
\else
   \usepackage[\MYhyperrefoptions,breaklinks=true,dvips]{hyperref}
   \usepackage{breakurl}                        % Allows 'dvips' driver to break links
\fi

@@

\usepackage[maxfloats=40]{morefloats}
\newcounter{todoidx}
% \setcounter{todoidx}

\ifTODO
   \definecolor{todobackground}{rgb}{0.95,0.95,0.95}
   \setlength\marginparsep{1pt}
   \setlength\marginparwidth{35pt}
   \newlength\marginparwidthsmall
   \setlength\marginparwidthsmall{\marginparwidth}
   \addtolength\marginparwidthsmall{-7pt}
   \newcommand\todo[1]{%
      \addtocounter{todoidx}{1}%
      {\color{Red}\bf(\thetodoidx{})}%%\fbox{\bf\thetodoidx{}}}%
      \marginpar{%
         {\vspace*{-10pt}\color{Red}\fbox{\bf\thetodoidx{}}}\\%
         \fcolorbox{red}{todobackground}{\parbox{\marginparwidthsmall}{\scriptsize #1}}}}

@@

\usepackage{float}

@@

\newcommand\Fig[1]{Fig.~\ref{#1}}

@@

\newcommand\Om{O_\text{m}}
\newcommand\Oa{O_\text{a}}
\newcommand\Nl{N_\text{l}}
\newcommand\Nk{N_\text{k}}
\newcommand\1{\vec 1}
\newcommand\I{\mat I}
\renewcommand*\a{\vec a}
\renewcommand*\i{\vec i}
\renewcommand*\k{\vec k}
\newcommand*\n{\vec n}
\newcommand*\p{\vec p}
\newcommand*\s{\vec s}
\newcommand*\w{\vec w}
\newcommand*\x{\vec x}
\newcommand*\y{\vec y}

@@

@@

\usepackage{tikz}
\usetikzlibrary{shapes,snakes}
\usepackage{amsmath,amssymb}
% \usepackage{datatool}
% \usepackage{glossaries}

\newenvironment{outline}
{\begin{itemize}}
{\end{itemize}}

@@

\begin{figure}[t]\centering%
\graphicsAI[drawing,width=\linewidth]{gfx/specs.svg}%
\caption{Simulator specifications.}\label{specs}%
\end{figure}

@@

\begin{figure*}[t]\centering%
\subfloat[SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.]{%
\graphicsAI[drawing,width=0.5\linewidth]{gfx/data_cylinder_submerged.svg}%
\label{data_cylinder}}%
\subfloat[Cylinder simulation with parameters estimated from SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.]{
\graphicsAI[drawing,width=0.5\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
\label{sim_cylinder}}%
\caption{A SAS image of a cylinder and a template simulation adapted to it.}
\end{figure*}

@@

\begin{figure*}[t]\centering%

\subfloat[Best template out of a predefined set. Inaccurate cylinder length, alignment and immersion depth. The segmented shadow and highlight regions are misaligned.]{
\graphicsAI[drawing,width=.5\linewidth]{gfx/overlay_cylinder_submerged.svg}\label{overlay_cylinder}%
}%
\hfil%
\subfloat[Adapted template. Template simulated with adapted parameters. Good fit in both highlight and shadow segments.]{%
\graphicsAI[width=.5\linewidth]{gfx/overlay_cylinder_submerged_adaptive.svg}%
}\caption[LoF entry]{Segmented simulation image overlaid the segmented SAS image. Segmentation overlay color description:\parbox{1cm}{\small\centering 1}}%
% % \hfill
% \parbox{1cm}{\small\centering
% \newline\centering\newline %\\[.5\baselineskip]
\begin{minipage}{.35\linewidth}
% \cdesc{800000}{Template highlight and image highlight}
% \cdesc{FF1000}{Template highlight only}
% \cdesc{FFEB00}{Image highlight only}
% \cdesc{83FF7C}{Background pixels}
\end{minipage}%
% \begin{minipage}{.35\linewidth}
% \cdesc{000083}{Template shadow and image shadow}
% \cdesc{0014FF}{Template shadow only}
% \cdesc{00EFFF}{Image shadow only}
% \cdesc{00A7FF}{Template shadow and image highlight}
% \end{minipage}
% }\label{overlay_cylinder_adaptive}%
% % \vspace{\baselineskip}
\caption{Segmented simulation image overlaid the segmented SAS image.}
\end{figure*}
